Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-08-05 chapters/chapter04.tex
removed repeating labels

We have developed a new simulation tool, called {\bussname}, that we consider to be a rejuvenation of Seq-Gen \citep{Rambaut1997}, with several extensions to better integrate with the BEAST inference framework.
Compared to Seq-Gen and other simulation software (Table~\ref{tab:Sim}), {\bussname} covers a relatively wide range of models while, similar to Mesquite, offering a cross-platform, user-friendly GUI.
{\bussname} is implemented in the Java programming language, and therefore requires a Java runtime environment, and depends on the BEAGLE library.
Although speed is unlikely to be an impeding factor in most simulation efforts, the core implementation using the BEAGLE library provides substantial increases in speed for large-scale simulations, in particular when invoking multi-core architecture to produce highly partitioned synthetic sequence data.

@@

\label{tab:Sim} 

>>>>

We have developed a new simulation tool, called {\bussname}, that we consider to be a rejuvenation of Seq-Gen \citep{Rambaut1997}, with several extensions to better integrate with the BEAST inference framework.
Compared to Seq-Gen and other simulation software (Table~\ref{tab:SimSoft}), {\bussname} covers a relatively wide range of models while, similar to Mesquite, offering a cross-platform, user-friendly GUI.
{\bussname} is implemented in the Java programming language, and therefore requires a Java runtime environment, and depends on the BEAGLE library.
Although speed is unlikely to be an impeding factor in most simulation efforts, the core implementation using the BEAGLE library provides substantial increases in speed for large-scale simulations, in particular when invoking multi-core architecture to produce highly partitioned synthetic sequence data.

@@

\label{tab:SimSoft} 
